\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-22 paper/algorithm.tex
fix: small fix for dominating definition

Given a query, \ProjectName{} produces a final set of possible plans

\begin{gather*}
 P= \{ p | \forall p'. \doms{p}{p'} \}
 \end{gather*}

@@

Given $\alpha$ and $P$, \ProjectName{} returns the $\alpha$-bound optimal plan in $P$. Note that the $\alpha$-bound optimal plan is unique, given that
$P$ only maintains dominating plans.

>>>>

Given a query, \ProjectName{} produces a final set of possible plans $P$ by only maintaining plans that are not dominated by others in the search space. So if
our search space is $S$

\begin{gather*}
 P= \{ p | \not\exists p' \in S. \doms{p'}{p} \}
 \end{gather*}

@@

Given $\alpha$ and $P$, \ProjectName{} returns the $\alpha$-bound optimal plan in $P$. Note that the $\alpha$-bound optimal plan is unique in $P$, given that
$P$ does not keep any plans dominated by others in the set.
